### 2025-08-30 sections/2-methods.tex
minor revisions
one less orphan

Starting from the root cluster $\mathcal{R}$ containing the entire dataset, Alg.~\ref{alg:methods:partition} gives us $\mathcal{T}$.
During this procedure, we also compute and cache the LFD of each cluster using Eq.~\ref{eq:methods:lfd-half}.

>>>>

Starting from the root cluster $\mathcal{R}$ containing the entire dataset, Alg.~\ref{alg:methods:partition} recursively builds $\mathcal{T}$.
During Partition, we also compute and cache the LFD of each cluster using Eq.~\ref{eq:methods:lfd-half}.
